|

### 2023-01-20 text/SupportManuscriptDraft.Rmd
Updates to text and suppl.
Submitted revised edition of manuscript

---
new_session: FALSE
title: |
  **Supporting Information: Towards individual-based pollination ecology: Automatic tracking of life histories of individual flowers**
author:
- Hjalte M. R. Mann
- Alexandros Iosifidis
- Toke T. Høye
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
  html_document:
    df_print: paged
fontfamily: mathpazo
fontsize: 12pt
geometry: margin = 1in
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{dcolumn}
- \usepackage{caption}
- \usepackage{float}
- \usepackage{afterpage}
- \usepackage{siunitx}
- \usepackage{amsmath}
keywords: Tracking, flowering phenology, Arctic
bibliography: ./library.bib
csl: ./journal-of-ecology.csl
---

@@

**Table S1:** Results of the filtering algorithm for filtering distances 5-500 with a stepsize of 50 for all three series.

![](../figures/FullFilteringDistanceTest.png){ width=100% }

>>>>

---
new_session: FALSE
title: |
  **Towards individual-based floral biology: Automatic tracking of life histories of individual flowers**
author:
- Hjalte M. R. Mann
- Alexandros Iosifidis
- Toke T. Høye
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
  html_document:
    df_print: paged
fontfamily: mathpazo
fontsize: 12pt
geometry: margin = 1in
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{dcolumn}
- \usepackage{caption}
- \usepackage{float}
- \usepackage{afterpage}
- \usepackage{siunitx}
- \usepackage{amsmath}
keywords: Tracking, flowering phenology, Arctic
bibliography: ./library.bib
csl: ./journal-of-ecology.csl
---

@@

# 2

## Results of the filtering algorithm for filtering distances (eps) 50-500 with a stepsize of 50 for the three series.

eps = 50: 158 mismatches with 171 tracks kept 
eps = 100: 103 mismatches with 153 tracks kept 
eps = 150: 71 mismatches with 130 tracks kept 
eps = 200: 47 mismatches with 106 tracks kept 
eps = 250: 30 mismatches with 75 tracks kept 
eps = 300: 9 mismatches with 51 tracks kept 
eps = 350: 0 mismatches with 28 tracks kept 
eps = 400: 0 mismatches with 18 tracks kept 
eps = 450: 0 mismatches with 16 tracks kept 
eps = 500: 0 mismatches with 11 tracks kept

#![](../figures/FullFilteringDistanceTest.png){width="100%"}
